Regular singular Volterra equations on complex domains

### 2023-07-23 reg-sing-volterra.tex
Revise hypotheses and function spaces
Argue that the new function spaces are complete. Since our exponential
weight isn't holomorphic, the argument is more involved than before.

%%\theoremstyle{definition}
\newtheorem{defn}{Definition}
\theoremstyle{plain}
%%\newtheorem{prop}{Proposition}
\newtheorem{thm}{Theorem}

@@

% symbology
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\let\Re\relax
\DeclareMathOperator{\Re}{Re}
\newcommand{\laplace}{\mathcal{L}}
\newcommand{\series}[1]{\tilde{#1}}
\newcommand{\fracderiv}[3]{\partial^{#1}_{#2, #3}}
\newcommand{\holoL}[1]{\mathcal{H}L^{#1}} %% may no longer be needed
\newcommand{\expHoloL}[2]{\mathcal{H}L^{#1}_{#2}} %% may no longer be needed
\DeclareMathOperator{\Ai}{Ai}

@@

\begin{document}
\maketitle
\section{Introduction}
\subsection{Motivation}\label{motivation}
In its most basic form, the Laplace transform $\laplace$ turns $L^1$ functions of a real ``position'' variable $\zeta$ into holomorphic functions of a complex ``frequency'' variable $z$. Through identities like
\begin{align*}
\frac{\partial}{\partial z} \laplace \varphi & = \laplace(z\varphi) \\
\laplace k\;\laplace f & = k * \varphi \\
z^{-\lambda} \laplace \varphi & = \laplace\,\fracderiv{-\lambda}{}{} \varphi,
\end{align*}
where $\fracderiv{-\lambda}{}{}$ is the Riemann-Liouville fractional integral of order $\lambda \in (0, \infty)$, the Laplace transform pulls differential operators on the frequency domain back to Volterra integral operators on the position domain. The favorable regularity properties and comprehensive theory of Volterra equations can thus be brought to bear on differential equations.

If we complexify the position variable $\zeta$, the functions on the position domain whose Laplace transforms satisfy a given differential equation will often extend holomorphically. \textbf{[...]}
\subsection{Main result}
\begin{defn}\label{fin-order}
Consider a Volterra operator $\mathcal{V}$ of the form
\[ [\mathcal{V}\varphi](a) = m(a)\,\varphi(a) + \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta. \]
We'll say $\mathcal{V}$ is {\em effectively finite-order} over a domain $\Omega$ if there are some $c, c' \in (0, \infty)$ for which
\begin{itemize}
\item $|m(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$
\item $|k(a, a')| \lesssim e^{c|\zeta(a)| + c'|\zeta(a')|}$ over all $a, a' \in \Omega$
\end{itemize}
and at one of the following holds:
\begin{enumerate}
\item\label{case:0th-order} $m$ isn't the zero function.
\item\label{case:pos-order} $m$ is the zero function, and there's some $\lambda \in (0, \infty)$ for which
\[ |k(a, a')| \in O_\text{\rm diag}\big( |\zeta(a) - \zeta(a')|^{\lambda-1} \big), \]
where {\rm ``diag''} means the diagonal in $\Omega^2$.
\end{enumerate}
We'll say $\mathcal{V}$ has order $0$ in case~\ref{case:0th-order}, and order at least $\lambda$ in case~\ref{case:pos-order}.
\end{defn}
\textcolor{DarkTurquoise}{The result below might not be stated perfectly, but it gives at least a rough sense of what I expect. It's an improved version of the result stated in Section~\ref{frac_int_exist}, which is copied from {\tt airy-resurgence}. Note that {\tt airy-resurgence} uses the opposite sign convention for the parameter $\sigma$ in $\holoL{\infty, \sigma}$.}
\begin{thm}
Let $\Omega$ be an acute-angled sector around $0$ in the complex plane. \textcolor{DarkTurquoise}{I don't think it's really necessary for $\Omega$ to have a sharp point at $0$, but the condition of being an acute-angled sector is sufficient and easy to state.}

Consider a Volterra operator
\[ \mathcal{V} = p + \partial^{-1} \circ q + \mathcal{R} \]
over $\Omega$ which can be decomposed, as shown above, into the sum of a zeroth-order part $p$, a first-order part $\partial^{-1} \circ q$, and an effectively higher-order part $\mathcal{R}$. To be precise, $\mathcal{R}$ is supposed to be an integral operator of the form
\[ [\mathcal{R}\varphi](a) = \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta \]
which is effectively finite-order over $\Omega$ in the sense of Definition~\ref{fin-order}, with order at least $1 + \epsilon$ for some $\epsilon \in (0, \infty)$.

Assume, furthermore, that:
\begin{itemize}
\item There's some $c \in (0, \infty)$ for which
$|p(a)| \lesssim e^{c|\zeta(a)|}$ and $|q(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$.
\item $p$ and $q$ extend holomorphically over $\zeta = 0$.
\item $p$ has a simple zero at $\zeta = 0$.
\end{itemize}
Let $p_1$ and $q_0$ be the values of $\tfrac{\partial}{\partial \zeta} p$ and $q$, respectively, at $\zeta = 0$.

Under these conditions, let's try to solve the regular singular Volterra equation
\[ \mathcal{V}f = 0. \]
The leading-order part of the equation,
\[ \big[p_1 \zeta + \partial^{-1} \circ q_0\big]f = 0, \]
has $\zeta^{\tau-1}$ as a solution, where $\tau = p_1/q_0$. If we guess that the function spaces defined in Section~\ref{fn-spaces} are well suited for this problem, we might hope for the full equation to have a solution of the form
\[ f = \zeta^{\tau-1} + f_*, \]
where $f_* \in \holoL{\infty, 1-\tau-\epsilon}_Z(\Omega)$ for some $Z \in \C$. When $Z\Omega$ is in the right half-plane and $|Z|$ is large enough, there is in fact a unique solution of this form.
\end{thm}
\section{Function spaces for holomorphic Volterra operators}\label{fn-spaces}
\subsection{Weighted holomorphic $L^\infty$ spaces}
Throughout this paper, as described in Section~\ref{motivation}, the ``position'' variable $\zeta$ will be the standard coordinate on $\C$. Take a simply connected open set $\Omega \subset \C$ that touches but doesn't contain $\zeta = 0$. Let $\holoL{\infty}(\Omega)$ be the space of bounded holomorphic functions on $\Omega$ with the supremum norm $\|\cdot\|_\infty$. For any $\sigma \in \R$ and $Z \in \C$, multiplying by $\zeta^\sigma e^{\Re(Z\zeta)}$ maps $\holoL{\infty}(\Omega)$ isomorphically onto another space of holomorphic functions on $\Omega$. We'll call this space $\expHoloL{\infty, \sigma}{Z}(\Omega)$ and give it the norm $\|f\|_{\infty, \sigma; Z} = \|\zeta^{-\sigma} e^{-\Re(Z\zeta)} f\|_\infty$, so that
\begin{align*}
\holoL{\infty}(\Omega) & \to \expHoloL{\infty, \sigma}{Z}(\Omega) \\
\varphi & \mapsto \zeta^\sigma e^{\Re(Z\zeta)} \varphi
\end{align*}
is an isometry. More generally,
\begin{align*}
\expHoloL{\infty, \rho}{Z}(\Omega) & \to \expHoloL{\infty, \rho+\delta}{Z}(\Omega) \\
f & \mapsto \zeta^\delta f
\end{align*}
is an isometry for all $\rho, \delta \in \R$ and $Z \in \C$. This reduces to the previous statement when $\rho = 0$ and $Z = 0$.
\subsection{Graded algebra structure}
For each $\delta \in [0, \infty)$, the functions in $\holoL{\infty, \rho}(\Omega)$ belong to $\holoL{\infty, \rho-\delta}(\Omega)$ too, and the inclusion map $\holoL{\infty, \rho}(\Omega) \hookrightarrow \holoL{\infty, \rho-\delta}(\Omega)$ has norm $\|\zeta^\delta\|_\infty$.
\begin{verify}
\begin{align*}
\|f\|_{\infty, \rho+\delta, Z} & = \|\zeta^{-(\rho-\delta)} e^{-\Re(Z\zeta)} f\|_\infty \\
& = \|\zeta^\delta \zeta^{-\rho} e^{-\Re(Z\zeta)} f\|_\infty \\
& = \|\zeta^\delta\|_\infty\,\|\zeta^{-\rho} e^{-\Re(Z\zeta)} f\|_\infty & \text{(Banach algebra)} \\
& \le \|\zeta^\delta\|_\infty\,\|f\|_{\infty, \rho; Z}
\end{align*}
\end{verify}
Since $\holoL{\infty}(\Omega)$ is a Banach algebra, the function space $\expHoloL{\infty, -\infty}{Z}(\Omega) := \bigcup_{\sigma \in \R} \expHoloL{\infty, \sigma}{Z}(\Omega)$ is a graded algebra, with a different norm on each grade. For each $\rho, \delta \in \R$, multiplication by a function $m \in \holoL{\infty, \delta}(\Omega)$ gives a map $\holoL{\infty, \rho}(\Omega) \to \holoL{\infty, \rho+\delta}(\Omega)$ with norm $\|m\|_{\infty, \delta}$.
\subsection{Norms of effectively finite-order operators}
\begin{itemize}
\item Say $|m(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$. For any $f \in \expHoloL{\infty, \rho}{Z}$,
\begin{align*}
\|mf\|_{\infty, \sigma; Z} =
\end{align*}
\end{itemize}

>>>>

%%\theoremstyle{definition}
\newtheorem{defn}{Definition}
\theoremstyle{plain}
\newtheorem{prop}{Proposition}
\newtheorem{thm}{Theorem}

@@

% symbology
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\let\Re\relax
\DeclareMathOperator{\Re}{Re}
\newcommand{\laplace}{\mathcal{L}}
\newcommand{\series}[1]{\tilde{#1}}
\newcommand{\fracderiv}[3]{\partial^{#1}_{#2, #3}}
\newcommand{\cont}{\mathcal{C}}
\newcommand{\holo}{\mathcal{H}}
\newcommand{\singexp}[2]{\mathcal{H}L^\infty_{#1, #2}}
\newcommand{\holoL}[1]{\mathcal{H}L^{#1}} %% may no longer be needed
\newcommand{\expHoloL}[2]{\mathcal{H}L^{#1}_{#2}} %% may no longer be needed
\DeclareMathOperator{\Ai}{Ai}

@@

\begin{document}
\maketitle
\section{Introduction}
\subsection{Motivation}\label{motivation}
In its most basic form, the Laplace transform $\laplace$ turns $L^1$ functions of a real ``position'' variable $\zeta$ into holomorphic functions of a complex ``frequency'' variable $z$. Through identities like
\begin{align*}
\frac{\partial}{\partial z} \laplace \varphi & = \laplace(z\varphi) \\
\laplace k\;\laplace \varphi & = \laplace(k * \varphi) \\
z^{-\lambda} \laplace \varphi & = \laplace\,\fracderiv{-\lambda}{}{} \varphi,
\end{align*}
where $\fracderiv{-\lambda}{}{}$ is the Riemann-Liouville fractional integral of order $\lambda \in (0, \infty)$, the Laplace transform pulls differential operators on the frequency domain back to Volterra integral operators on the position domain. The favorable regularity properties and comprehensive theory of Volterra equations can thus be brought to bear on differential equations.

If we complexify the position variable $\zeta$, the functions on the position domain whose Laplace transforms satisfy a given differential equation will often extend holomorphically. \textbf{[...]}
\subsection{Main result}
%%\begin{defn}\label{fin-order}
%%Consider a Volterra operator $\mathcal{V}$ of the form
%%\[ [\mathcal{V}\varphi](a) = m(a)\,\varphi(a) + \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta. \]
%%We'll say $\mathcal{V}$ is {\em effectively finite-order} over a domain $\Omega$ if there are some $c, c' \in (0, \infty)$ for which
%%\begin{itemize}
%%\item $|m(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$
%%\item $|k(a, a')| \lesssim e^{c|\zeta(a)| + c'|\zeta(a')|}$ over all $a, a' \in \Omega$
%%\end{itemize}
%%and at one of the following holds:
%%\begin{enumerate}
%%\item\label{case:0th-order} $m$ isn't the zero function.
%%\item\label{case:pos-order} $m$ is the zero function, and there's some $\lambda \in (0, \infty)$ for which
%%\[ |k(a, a')| \in O_\text{\rm diag}\big( |\zeta(a) - \zeta(a')|^{\lambda-1} \big), \]
%%where {\rm ``diag''} means the diagonal in $\Omega^2$.
%%\end{enumerate}
%%We'll say $\mathcal{V}$ has order $0$ in case~\ref{case:0th-order}, and order at least $\lambda$ in case~\ref{case:pos-order}.
%%\end{defn}
\textcolor{DarkTurquoise}{The result below might not be stated perfectly, but it gives at least a rough sense of what I expect. It's an improved version of the result stated in Section~\ref{frac_int_exist}, which is copied from {\tt airy-resurgence}. Note that {\tt airy-resurgence} uses the opposite sign convention for the parameter $\sigma$ in $\holoL{\infty, \sigma}$.}
\begin{thm}
Let $\Omega$ be an acute-angled open sector around $\zeta = 0$ in the complex plane. \textcolor{DarkTurquoise}{I don't think it's really necessary for $\Omega$ to have a sharp point at $0$, but the condition of being an acute-angled sector is sufficient and easy to state.} Over $\Omega$, consider a Volterra operator
\[ \mathcal{V} = p + \partial^{-1} \circ q + \mathcal{R}, \]
where
\begin{itemize}
\item $p$ is a holomorphic function on $\Omega$ that extends holomorphically over $\zeta = 0$, with
\begin{itemize}
\item a simple zero at $\zeta = 0$,
\item no zeros in $\Omega$ (as the next condition implies), and
\item a positive lower bound $C_p |z|^d \le |p|$;
\end{itemize}
\item $q$ is a holomorphic function on $\Omega$ that extends holomorphically over $\zeta = 0$, with
\begin{itemize}
\item an upper bound $|q| \le C_q |z|^{d-1}$; and
\end{itemize}
\item $\mathcal{R}$ is an integral kernel operator
\[ [\mathcal{R}\varphi](a) = \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta, \]
where $k$ is a holomorphic function on $\Omega^2$, with
\begin{itemize}
\item an exponential upper bound $k(a, a') \le C_k e^{A|\zeta(a) - \zeta(a')|}$.
\end{itemize}
\end{itemize}
Let $p_1$ and $q_0$ be the values of $\tfrac{\partial}{\partial \zeta} p$ and $q$, respectively, at $\zeta = 0$, and let $\tau = q_0 / p_1$.

For any $\epsilon > 0$, when the constant $\Lambda > A$ is large enough, the regular singular Volterra equation
\[ \mathcal{V}f = 0 \]
has a unique solution in the affine subspace
\[ \zeta^{\tau-1} + \holoL{\infty, \tau-1+\epsilon}_\Lambda(\Omega) \]
of the function space $\holoL{\infty, \tau-1}_\Lambda(\Omega)$, defined in Section~\ref{fn-spaces}.
\end{thm}
%%\begin{thm}
%%Let $\Omega$ be an acute-angled sector around $0$ in the complex plane. \textcolor{DarkTurquoise}{I don't think it's really necessary for $\Omega$ to have a sharp point at $0$, but the condition of being an acute-angled sector is sufficient and easy to state.}

%%Consider a Volterra operator
%%\[ \mathcal{V} = p + \partial^{-1} \circ q + \mathcal{R} \]
%%over $\Omega$ which can be decomposed, as shown above, into the sum of a zeroth-order part $p$, a first-order part $\partial^{-1} \circ q$, and an effectively higher-order part $\mathcal{R}$. To be precise, $\mathcal{R}$ is supposed to be an integral operator of the form
%%\[ [\mathcal{R}\varphi](a) = \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta \]
%%which is effectively finite-order over $\Omega$ in the sense of Definition~\ref{fin-order}, with order at least $1 + \epsilon$ for some $\epsilon \in (0, \infty)$.

%%Assume, furthermore, that:
%%\begin{itemize}
%%\item There's some $c \in (0, \infty)$ for which
%%$|p(a)| \lesssim e^{c|\zeta(a)|}$ and $|q(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$.
%%\item $p$ and $q$ extend holomorphically over $\zeta = 0$.
%%\item $p$ has a simple zero at $\zeta = 0$.
%%\end{itemize}
%%Let $p_1$ and $q_0$ be the values of $\tfrac{\partial}{\partial \zeta} p$ and $q$, respectively, at $\zeta = 0$.

%%Under these conditions, let's try to solve the regular singular Volterra equation
%%\[ \mathcal{V}f = 0. \]
%%The leading-order part of the equation,
%%\[ \big[p_1 \zeta + \partial^{-1} \circ q_0\big]f = 0, \]
%%has $\zeta^{\tau-1}$ as a solution, where $\tau = p_1/q_0$. If we guess that the function spaces defined in Section~\ref{fn-spaces} are well suited for this problem, we might hope for the full equation to have a solution of the form
%%\[ f = \zeta^{\tau-1} + f_*, \]
%%where $f_* \in \holoL{\infty, 1-\tau-\epsilon}_Z(\Omega)$ for some $Z \in \C$. When $Z\Omega$ is in the right half-plane and $|Z|$ is large enough, there is in fact a unique solution of this form.
%%\end{thm}
\section{Function spaces for holomorphic Volterra operators}\label{fn-spaces}
\subsection{Weighted holomorphic $L^\infty$ spaces}
Throughout this paper, as described in Section~\ref{motivation}, the ``position'' variable $\zeta$ will be the standard coordinate on $\C$. Take a simply connected open set $\Omega \subset \C$ that touches but doesn't contain $\zeta = 0$. Let $\cont(\Omega)$ be the space of continuous complex-valued functions on $\Omega$. Give $\cont(\Omega)$ the compact-open topology, recalling that this is the finest topology in which the seminorm $f \mapsto \sup_K |f|$ is continuous for every compact subset $K \subset \Omega$~\cite[Example~2.6 and \S 4 notes]{fnl-cpx-anal}. The holomorphic functions form a closed subspace $\holo(\Omega) \subset \cont(\Omega)$~\cite[Proposition~3.14]{fnl-cpx-anal}\textcolor{orange}{[Luecking \& Rubel]}.

Fixing a real constant $\Lambda$, let's restrict our attention to holomorphic functions on $\Omega$ which are bounded by constant multiples of $e^{\Lambda|\zeta|}$. One might describe these functions as being uniformly of exponential type $\Lambda$. They form a space $\singexp{0}{\Lambda}(\Omega)$, which we'll equip with the norm $\|f\|_{0,\Lambda} = \sup_\Omega e^{-\Lambda|\zeta|}\,|f|$. With respect to the seminorm on $\holo(\Omega)$ given by a compact set $K \subset \Omega$, the inclusion map $\singexp{0}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ has norm $\sup_K e^{\Lambda |\zeta|}$. That means the inclusion is continuous.
\begin{prop}\label{exp-complete}
The space $\singexp{0}{\Lambda}(\Omega)$ is complete.
\end{prop}
\begin{proof}
\textcolor{orange}{[Check!]} Take a Cauchy sequence $f_1, f_2, f_3, \ldots \in \singexp{0}{\Lambda}(\Omega)$. The inclusion map $\singexp{0}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is bounded with respect to each of the seminorms on $\holo(\Omega)$, as discussed above, so our sequence is Cauchy in $\holo(\Omega)$ too. Since $\holo(\Omega)$ is complete~\cite[Proposition~3.5]{fnl-cpx-anal}, our sequence converges to a function $f$ there.

The Cauchy property in $\singexp{0}{\Lambda}(\Omega)$ tells us that for any $r > 0$, we can find some $n$ for which $e^{-\Lambda |\zeta|} |f_k - f_n| \le r$ whenever $k \ge n$. Since convergence in $\holo(\Omega)$ implies pointwise convergence, we can see as $k$ grows that $e^{-\Lambda |\zeta|} |f - f_n| \le r$. This shows that our sequence converges to $f$ in the norm $\|\cdot\|_{0,\Lambda}$. We can also use the Cauchy property in $\singexp{0}{\Lambda}(\Omega)$ to bound the norms $\|f_n\|_{0,\Lambda}$. Then, from the pointwise convergence argument above, we can draw the additional conclusion that $f$ is in $\singexp{0}{\Lambda}(\Omega)$.
\end{proof}

Now, let's relax our norm to allow both exponential growth at infinity and a power-law singularity at $\zeta = 0$. Let $\singexp{\sigma}{\Lambda}(\Omega)$ be the space of holomorphic functions on $\Omega$ which are bounded by constant multiples of $|\zeta|^\sigma e^{\Lambda|\zeta|}$. Give it the norm $\|f\|_{\sigma,\Lambda} = \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|$. Reprising the arguments from above, we can show that the inclusion $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is continuous, and we can generalize Proposition~\ref{exp-complete}:
\begin{prop}
The space $\singexp{\sigma}{\Lambda}(\Omega)$ is complete.
\end{prop}
%%Let $\holoL{\infty}(\Omega)$ be the space of bounded holomorphic functions on $\Omega$ with the supremum norm $\|\cdot\|_\infty$. For any $\sigma \in \R$ and $Z \in \C$, multiplying by $\zeta^\sigma e^{\Re(Z\zeta)}$ maps $\holoL{\infty}(\Omega)$ isomorphically onto another space of holomorphic functions on $\Omega$. We'll call this space $\expHoloL{\infty, \sigma}{Z}(\Omega)$ and give it the norm $\|f\|_{\infty, \sigma; Z} = \|\zeta^{-\sigma} e^{-\Re(Z\zeta)} f\|_\infty$, so that
%%\begin{align*}
%%\holoL{\infty}(\Omega) & \to \expHoloL{\infty, \sigma}{Z}(\Omega) \\
%%\varphi & \mapsto \zeta^\sigma e^{\Re(Z\zeta)} \varphi
%%\end{align*}
%%is an isometry. More generally,
%%\begin{align*}
%%\expHoloL{\infty, \rho}{Z}(\Omega) & \to \expHoloL{\infty, \rho+\delta}{Z}(\Omega) \\
%%f & \mapsto \zeta^\delta f
%%\end{align*}
%%is an isometry for all $\rho, \delta \in \R$ and $Z \in \C$. This reduces to the previous statement when $\rho = 0$ and $Z = 0$.
\subsection{Graded algebra structure}
For each $\delta \in [0, \infty)$, the functions in $\holoL{\infty, \rho}(\Omega)$ belong to $\holoL{\infty, \rho-\delta}(\Omega)$ too, and the inclusion map $\holoL{\infty, \rho}(\Omega) \hookrightarrow \holoL{\infty, \rho-\delta}(\Omega)$ has norm $\|\zeta^\delta\|_\infty$.
\begin{verify}
\begin{align*}
\|f\|_{\infty, \rho+\delta, Z} & = \|\zeta^{-(\rho-\delta)} e^{-\Re(Z\zeta)} f\|_\infty \\
& = \|\zeta^\delta \zeta^{-\rho} e^{-\Re(Z\zeta)} f\|_\infty \\
& = \|\zeta^\delta\|_\infty\,\|\zeta^{-\rho} e^{-\Re(Z\zeta)} f\|_\infty & \text{(Banach algebra)} \\
& \le \|\zeta^\delta\|_\infty\,\|f\|_{\infty, \rho; Z}
\end{align*}
\end{verify}
Since $\holoL{\infty}(\Omega)$ is a Banach algebra, the function space $\expHoloL{\infty, -\infty}{Z}(\Omega) := \bigcup_{\sigma \in \R} \expHoloL{\infty, \sigma}{Z}(\Omega)$ is a graded algebra, with a different norm on each grade. For each $\rho, \delta \in \R$, multiplication by a function $m \in \holoL{\infty, \delta}(\Omega)$ gives a map $\holoL{\infty, \rho}(\Omega) \to \holoL{\infty, \rho+\delta}(\Omega)$ with norm $\|m\|_{\infty, \delta}$.
\subsection{Norms of effectively finite-order operators}
\begin{itemize}
\item Say $|m(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$. For any $f \in \expHoloL{\infty, \rho}{Z}$,
\begin{align*}
\|mf\|_{\infty, \sigma; Z} =
\end{align*}
\end{itemize}
